Analysis of NLA17 Dissolved Gas Indicator

### 2023-02-08 scripts/dgIndicatorAnalysis.Rmd

```{r results='hide', message=FALSE, warning=FALSE}
# load libraries
library(sf) # spatial data
library(gstat) # lagged scatterplot, variogram
library(tidyverse) # dplyr, ggplot
library(janitor) # clean names
library(spdep) # k-NN and Moran plot
library(ncf) # ncf::correlogram
library(lattice) # xyplot
library(micromap) # linked micromaps
library(tictoc)

>>>>

```{r results='hide', message=FALSE, warning=FALSE}
# load libraries
library(sf) # spatial data
library(gstat) # lagged scatterplot, variogram
library(tidyverse) # dplyr, ggplot
library(janitor) # clean names
library(spdep) # k-NN and Moran plot
library(ncf) # ncf::correlogram
library(lattice) # xyplot
library(micromap) # linked micromaps
library(tictoc)
library(spmodel) # esv function
